\begin{thebibliography}{9}

\bibitem{A} \label{thepaper} Kulkarni, Sayali, et al. ``Collective annotation of Wikipedia entities in web text.'' Proceedings of the 15th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2009.

\bibitem{B}  \label{thesite} \url{http://www.cse.iitb.ac.in/~soumen/OWI/Slides/}

\bibitem{C} \label{thesurvey} William Cohen's Survey available at \ref{thesite}

\bibitem{The Wikipedia Page} \label{thewiki} \url{http://en.wikipedia.org/wiki/Named-entity_recognition}
\bibitem{D} \label{stanfordner} \url{http://nlp.stanford.edu/software/CRF-NER.shtml}

\bibitem{E} 

\label{mw}
Milne, David, and Ian H. Witten. ``Learning to link with wikipedia.'' Proceedings of the 17th ACM conference on Information and knowledge management. ACM, 2008.

\bibitem{F}{ws} \label{ws} \url{http://www.worldwidewebsize.com/}

\bibitem{G} \label{wikistats} \url{http://en.wikipedia.org/wiki/Wikipedia:Statistics}

\bibitem{F} \label{wikify}
Mihalcea, Rada, and Andras Csomai. ``Wikify!: linking documents to encyclopedic knowledge.'' Proceedings of the sixteenth ACM conference on Conference on information and knowledge management. ACM, 2007.

\bibitem{H} \label{aida}
Hoffart, Johannes, et al. ``Robust disambiguation of named entities in text.'' Proceedings of the Conference on Empirical Methods in Natural Language Processing. Association for Computational Linguistics, 2011.

\bibitem{I} \label{kpsim}
Hoffart, Johannes, et al. "Kore: keyphrase overlap relatedness for entity disambiguation." Proceedings of the 21st ACM international conference on Information and knowledge management. ACM, 2012.

\bibitem{J} \label{relgram}
Balasubramanian, Niranjan, Stephen Soderland, and Oren Etzioni. "Rel-grams: a probabilistic model of relations in text." Proceedings of the Joint Workshop on Automatic Knowledge Base Construction and Web-scale Knowledge Extraction. Association for Computational Linguistics, 2012.
\end{thebibliography}