\begin{thebibliography}{9}

\bibitem{A} \label{thepaper} Kulkarni, Sayali, et al. ``Collective annotation of Wikipedia entities in web text.'' Proceedings of the 15th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2009.

\bibitem{B}  \label{thesite} \url{http://www.cse.iitb.ac.in/~soumen/OWI/Slides/}

\bibitem{C} \label{thesurvey} William Cohen's Survey available at \ref{thesite}

\bibitem{The Wikipedia Page} \label{thewiki} \url{http://en.wikipedia.org/wiki/Named-entity_recognition}
\bibitem{D} \label{stanfordner} \url{http://nlp.stanford.edu/software/CRF-NER.shtml}

\bibitem{E} 

\label{mw}
Milne, David, and Ian H. Witten. ``Learning to link with wikipedia.'' Proceedings of the 17th ACM conference on Information and knowledge management. ACM, 2008.

\bibitem{F}{ws} \label{ws} \url{http://www.worldwidewebsize.com/}

\bibitem{G} \label{wikistats} \url{http://en.wikipedia.org/wiki/Wikipedia:Statistics}

\bibitem{F} \label{wikify}
Mihalcea, Rada, and Andras Csomai. ``Wikify!: linking documents to encyclopedic knowledge.'' Proceedings of the sixteenth ACM conference on Conference on information and knowledge management. ACM, 2007.

\bibitem{H} \label{aida}
Hoffart, Johannes, et al. ``Robust disambiguation of named entities in text.'' Proceedings of the Conference on Empirical Methods in Natural Language Processing. Association for Computational Linguistics, 2011.

\bibitem{I} \label{kpsim}
Hoffart, Johannes, et al. "Kore: keyphrase overlap relatedness for entity disambiguation." Proceedings of the 21st ACM international conference on Information and knowledge management. ACM, 2012.

\bibitem{J} \label{relgram}
Balasubramanian, Niranjan, Stephen Soderland, and Oren Etzioni. "Rel-grams: a probabilistic model of relations in text." Proceedings of the Joint Workshop on Automatic Knowledge Base Construction and Web-scale Knowledge Extraction. Association for Computational Linguistics, 2012.

\bibitem{H} \label{cohschemas}
Balasubramanian, Niranjan, Stephen Soderland, and Oren Etzioni Mausam. "Generating Coherent Event Schemas at Scale." Proceedings of the Empirical Methods in Natural Language Processing. ACM (2013).

\bibitem{I} \label{lesk}
Michael Lesk. 1986. Automatic sense disambiguation using machine readable dictionaries: how to tell a pine cone from an ice cream cone. In Proceedings of the 5th annual international conference on Systems documentation (SIGDOC '86), Virginia DeBuys (Ed.). ACM, New York, NY, USA, 24-26. DOI=10.1145/318723.318728 http://doi.acm.org/10.1145/318723.318728

\bibitem{J} \label{wordnet}
http://wordnet.princeton.edu/wordnet/

\bibitem{K} \label{yago}
Suchanek, Fabian M., Gjergji Kasneci, and Gerhard Weikum. "Yago: a core of semantic knowledge." Proceedings of the 16th international conference on World Wide Web. ACM, 2007.

\bibitem{L} \label{dbpedia}
Auer, Sören, et al. "Dbpedia: A nucleus for a web of open data." The semantic web. Springer Berlin Heidelberg, 2007. 722-735.

\bibitem{M} \label{patty}
Nakashole, Ndapandula, Gerhard Weikum, and Fabian Suchanek. "PATTY: a taxonomy of relational patterns with semantic types." Proceedings of the 2012 Joint Conference on Empirical Methods in Natural Language Processing and Computational Natural Language Learning. Association for Computational Linguistics, 2012.

\bibitem{N} \label{freebase}
Bollacker, Kurt, et al. "Freebase: a collaboratively created graph database for structuring human knowledge." Proceedings of the 2008 ACM SIGMOD international conference on Management of data. ACM, 2008.

\bibitem{O} \label{mmd}
Iyer, Arun, Saketha Nath, and Sunita Sarawagi. "Maximum Mean Discrepancy for Class Ratio Estimation: Convergence Bounds and Kernel Selection." Proceedings of The 31st International Conference on Machine Learning. 2014.

\bibitem{Q} \label{aidafeature}
Using Structured learning for named entity disambiguation, \url{http://www.cse.iitb.ac.in/~amanmadaan/docs/rnd/structentity.pdf}
\end{thebibliography}