%sg
\documentclass[a4paper,10pt]{report}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{url}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{epigraph}
\usepackage{graphicx, float}
\usepackage{pst-node}
\usepackage[]{algorithm2e}
\newtheorem{mydef}{Definition}
% Title Page
\title{Seminar Report\footnote{Draft}}
\author{Aman Madaan \\ 133050004}


\begin{document}
\maketitle
\tableofcontents

\begin{abstract}
TODO
\end{abstract}

\part{Problem Definition and Motivation}
\input{nedintro}

\part{Structured Knowledge Repositories}
\input{kb.tex}

\part{Named Entity Disambiguation}
\input{lned.tex}
\input{ned.tex}

\part{Aggregate Statistics}
\input{aggregate}

\chapter{Conclusion and further readings}
TODO

For this report, only a small subset of the papers was selected to cover as much ground as possible.
The following list may be valuable to the interested readers.

\begin{itemize}
 \item \textbf{We have emphasized on Wikipedia as the catalog. The following work presents a general approach} \\
 Sil, Avirup, et al. "Linking named entities to any database." Proceedings of the 2012 Joint Conference on Empirical Methods in Natural Language Processing and Computational Natural Language Learning. Association for Computational Linguistics, 2012.
 \item \textbf{Large scale named entity disambiguation.} \\
 Cucerzan, Silviu. ``Large-Scale Named Entity Disambiguation Based on Wikipedia Data.'' EMNLP-CoNLL. Vol. 7. 2007.
 \item \textbf{One of the initial works on NED} \\
 Bunescu, Razvan C., and Marius Pasca. "Using Encyclopedic Knowledge for Named entity Disambiguation." EACL. Vol. 6. 2006.
 \item \textbf{Yago, a clean catalog of Wikipedia entities and the relations } \\
 Suchanek, Fabian M., Gjergji Kasneci, and Gerhard Weikum. "Yago: a core of semantic knowledge." Proceedings of the 16th international conference on World Wide Web. ACM, 2007.
 \item \textbf{Quick entity annotations for short text} \\
 Suchanek, Fabian M., Gjergji Kasneci, and Gerhard Weikum. "Yago: a core of semantic knowledge." Proceedings of the 16th international conference on World Wide Web. ACM, 2007.
\end{itemize}


\input{bib}
\end{document}          
